\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-22 paper/ms.tex
nojss
Using bibtex as the journal wants

\documentclass[article]{jss}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}
\usepackage{dsfont}

@@

\section{Introduction}
Bayesian inference, where probability theory describes degrees of
logical implication or subjective certainty, provides a powerful general basis
for data analysis \citep{ohagan, sivia}. The result of such
an analysis is typically
posterior probabilities of various hypotheses, or
a joint posterior probability distribution for the values of unknown
parameters.

@@

Nested Sampling \citep[NS;][]{skilling} is a Monte Carlo method whose main
aim is to calculate $Z$. However, it can also be used to generate samples
to represent the posterior distribution $\pi(\theta)L(\theta)/Z$, or
any other distribution proportional to
$\pi(\theta)\Phi\left[L(\theta)\right]$ where $\Phi$ is any monotonic function.
This latter property makes NS particularly useful for statistical mechanics
calculations \citep{2009arXiv0906.3544P, 2015arXiv150303404B}, where the
``canonical'' family of distributions proportional to
$\pi(\theta)L(\theta)^\beta$ is of interest. In such applications,
$L(\theta)$ is usually equivalent to
$\exp(-\textnormal{energy})$. NS is particularly efficient for this, since
only a single run (exploring regions of higher and higher $L$) is needed, and different canonical
distributions can be obtained by re-weighting the output points.

@@

Sampling from the constrained priors (Equation~\ref{eqn:constrained_prior})
is required, and Markov Chain Monte Carlo (MCMC) is a popular method of doing
this, although alternatives exist \citep[e.g.][]{multinest, 2015MNRAS.453.4384H}.
Diffusive Nested Sampling \citep[DNS][]{dnest} is an alternative to NS for
problems where MCMC is the only viable sampling method. DNS is based on the
Metropolis algorithm, and evolves one or more particles in the parameter space, along with
an integer index variable $j$ for each particle,
to explore the following joint distribution:
\begin{align}
p(\theta, j) &= p(j)p(\theta | j)\\
&= w_j \times
\frac{\pi(\theta)\mathds{1}\left[L(\theta) > \ell_j\right]}{X(\ell_j)}.
\label{eqn:target_distribution}
\end{align}
where the $\{\ell_j\}$ are a sequence of increasing likelihood thresholds
or {\em levels},
$\ell_0 = 0$, and $\{w_j\}$ is the marginal distribution for $j$.
The marginal distribution for $\theta$ is then a {\em mixture} of
constrained priors:
\begin{align}
p(\theta) &=
\pi(\theta)\sum_{j=0}^{j_{\rm max}}
\frac{w_j\mathds{1}\left[L(\theta) > \ell_j\right]}{X(\ell_j)}.
\label{eqn:mixture_of_constrained_priors}
\end{align}
The DNS algorithm consists of two stages. In the first stage,
the particle(s) are initialized from the prior $\pi(\theta)$, equivalent
to the mixture of constrained priors with a single level whose log likelihood
threshold is $-\infty$. The mixture of constrained priors evolves by adding new levels,
each of which compresses the distribution by a factor of about $e \approx 2.71818$
(see \citet{dnest} for details). In this stage,
the mixture weights $\{w_j\}$ are set according to
\begin{align}
w_j &\propto \exp(j/\lambda),\label{eqn:weighting}
\end{align}
where $\lambda$ is a scale length.
This enhances the probability that particles stay close to the
highest likelihood regions seen.
The second stage sets the mixture weights to be approximately
uniform ($w_j \propto 1$), with some tweaks described by \citet{dnest}.

The mixture of constrained priors tends to be easier to sample than the
posterior, as the prior is always a mixture component, allowing the
MCMC chain to mix between different modes in some circumstances. The marginal
likelihood estimate can also be more accurate than standard MCMC-based NS
\citep{dnest}, as less information is discarded.
DNS has been applied several times in astrophysics
\citep[e.g.][]{2014MNRAS.445.3055P, 2015ApJ...810...66H, 2015MNRAS.448.3206B}
and was recently used in a biological application \citep{salmonella}.

@@

The second column contains the log likelihoods of the levels.
The first level, with a $\log(X)$ value of 0 and a log likelihood of
$-10^{308}$ (basically ``minus infinity''), is simply the prior. The third
column has the ``tiebreaker'' values for the levels, which again are not
particularly useful unless your problem has likelihood plateaus. The fourth
and fifth columns are the number of accepted proposals and the total number
of proposals that have occurred within each level, which are useful for
monitoring the Metropolis acceptance ratio as a function of level.
The final two columns, called ``exceeds'', and ``visits'', are used to refine
the estimates of the level compressions (and hence the $\log(X)$ values of
the levels in column 1), as discussed in Section 3 of \citet{dnest}. The visits column counts the number of times a level (level $j$, say)
has been visited, but only starts counting after the next level ($j+1$) has been created. The exceeds column counts the number of times a particle that was
in level $j$ had a likelihood that exceeded that of level $j+1$.

@@

As described by \citet{skilling}, there is no guarantee in principle that
another peak might have appeared had a run continued for longer. These
{\em phase changes} are more common in statistical mechanics problems than
in data analysis problems, but can appear in the latter
\citep[e.g.][]{rjobject, 2015MNRAS.448.3206B}.

@@

\subsection{Equal weight enforcement}
This value is the parameter $\beta$ described in \citet{dnest}, and compensates
for imprecision in the spacing of the levels, so that the desired mixture
weights $w_j \propto 1$ are achieved during the second stage of the DNS
algorithm. The value 100 is recommended.

@@

Rather than trying to adapt proposal distributions as a function of level,
it is much simpler to just use heavy-tailed proposals which have some
probability of making a jump of appropriate size. This is slightly
wasteful of CPU time, but it saves a lot of human time and is more
fail-safe than tuned step sizes.
In simple experiments, we have found that heavy-tailed proposals are
about as efficient as slice sampling \citep{slice}, but much easier to
implement. The following procedure generates
$x$ from a heavy-tailed distribution:

@@

\section{Finite Mixture Models with RJObject}
Mixture models are a useful way of representing realistic prior information
in Bayesian data analysis. To reduce the amount of effort needed to
implement mixture models in DNS, \citet{rjobject} implemented
a template class called \code{RJObject} to handle the MCMC moves
required. The RJ in \code{RJObject} stands for Reversible Jump \citep{green}, as
\code{RJObject} implements birth and death moves for mixture
models with an unknown number of components. An updated version of
\code{RJObject} is included in \pkg{DNest4}.

@@

\citet{rjobject} described the motivation for \code{RJObject} and some details
about the Metropolis proposals underlying it. Here, we demonstrate how to
implement a finite mixture model using \code{RJObject}.
This example can be found in the
{\tt code/Examples/RJObject\_1DMixture}
directory. The ``SineWave'' and ``GalaxyField'' models
from \citet{rjobject} are also included in the \pkg{DNest4} repository.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.7\textwidth]{figures/galaxies_fig3.pdf}
\caption{The log-likelihood and posterior weights as a function
of compression $X$ for the galaxy data. There are phase changes
\citep{skilling} for which Nested Sampling is the best known
solution.
\label{fig:galaxies_fig3}}
\end{figure}

@@

A simple ``rejection sampling'' version of
ABC works by sampling the joint prior distribution for the parameters and
data
\begin{align}
p(\theta, D | M) &= p(\theta | M)p(D | \theta, M)
\end{align}
and rejecting samples for which $D \neq D_{\rm observed}$, so that the
samples represent
\begin{align}
p(\theta, D | D = D_{\rm observed}, M) &\propto p(\theta | M)p(D | \theta, M)
\mathds{1}\left[D = D_{\rm observed}\right].\label{eqn:abc_posterior}
\end{align}
The marginal distribution for $\theta$ is also the conditional distribution
$p(\theta | D = D_{\rm observed}, M)$, that is,
the posterior\footnote{Incidentally, this usage of the {\em joint} posterior
distribution for the parameters {\em and the data} provides a bridge
connecting Bayesian updating to maximum entropy updating \citep{caticha,giffin}.}.

@@

The main challenges associated with ABC are:
\begin{enumerate}[(i)]
\item The choice of discrepancy function $\rho(D; D_{\rm observed})$, which
may involve a choice of summary statistics,
\item How to choose the value of $\epsilon$, or how to change it as a run
progresses,
\item How to make algorithms more efficient than rejection sampling.
\end{enumerate}
Challenge (i) is Bayesian in nature, i.e. it relates to the very
definition of the posterior distribution itself.
On the other hand, challenges (ii) and (iii) are about the computational
implementation. Most ABC analyses are done using Sequential Monte Carlo
\citep[SMC; ][]{delmoral}, another family of algorithms closely related
to Nested Sampling and annealing in the sense that they work with
sequences of probability distributions.

\subsection{ABC with Nested Sampling}
NS can be used for ABC by noting that Equation~\ref{eqn:abc_posterior}
is of the same form as a constrained prior, only instead of being the prior
for the parameters $p(\theta | M)$ defined on the parameter space, it is
the {\em joint prior} for the parameters and the data,
$p(\theta, D |M) = p(\theta | M)p(D | \theta, M)$, defined on the product
space of possible parameters and datasets. Therefore, to implement
ABC in \pkg{DNest4}, you implement a model class
whose \code{from\_prior} member function generates parameters {\em and simulated
data} from the joint prior, and whose \code{perturb} member function
proposes changes to the parameters and/or the simulated data, in a
manner consistent with the joint prior. The \code{log\_likelihood} function
of the class, instead of actually evaluating the log likelihood, should
evaluate $-\rho(D; D_{\rm observed})$. Then, running the sampler
will create levels which systematically decrease $\rho$. The samples from
a particular level then represent the ABC posterior defined in
Equation~\ref{eqn:abc_posterior} with $\epsilon$ corresponding to minus
the ``log likelihood'' of the level.
A single \pkg{DNest4} run allows you to test sensitivity
to the value of $\epsilon$ using a single run.
The marginal likelihood reported will be
the probability that $\rho\left(D; D_{\rm observed}\right) < \epsilon$
given the model, although caution should be applied if
using this for model selection \citep{robert}.

@@

\begin{thebibliography}{99}
\bibitem[Baldock et al.(2015)]{2015arXiv150303404B} Baldock, R.~J.~N., 
P{\'a}rtay, L.~v.~B., Bart{\'o}k, A.~P., Payne, M.~C., Cs{\'a}nyi, G.\ 
2015.\ Determining pressure-temperature phase diagrams of materials.\ ArXiv 
e-prints arXiv: 1503.03404.

\bibitem[\protect\citeauthoryear{Brewer, P{\'a}rtay,
\& Cs{\'a}nyi}{2011}]{dnest} Brewer B.~J., P{\'a}rtay L.~B., Cs{\'a}nyi G., 2011,
Statistics and Computing, 21, 4, 649-656. arXiv:0912.2380

\bibitem[Brewer(2014)]{rjobject} Brewer, B.~J.\ 2014.\ Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling.\ ArXiv e-prints arXiv:1411.3921.

\bibitem[Brewer and Donovan(2015)]{2015MNRAS.448.3206B} Brewer, B.~J., Donovan, C.~P.\ 2015.\ Fast Bayesian inference for exoplanet discovery in radial velocity data.\ Monthly Notices of the Royal Astronomical Society 448, 3206-3214.

\bibitem[Caticha and Giffin(2006)]{caticha} Caticha, A., Giffin, A.\ 2006.\ Updating Probabilities.\ Bayesian Inference and Maximum Entropy Methods In Science and Engineering 872, 31-42.

\bibitem[Del Moral et al(2012)]{delmoral}
Del Moral, P., Doucet, A. and Jasra, A., 2012. An adaptive sequential Monte Carlo method for approximate Bayesian computation. Statistics and Computing, 22(5), pp.1009-1020.

\bibitem[Dybowski et al(2015)]{salmonella}
Dybowski, Richard, et al. Single passage in mouse organs enhances the survival and spread of Salmonella enterica. Journal of The Royal Society Interface 12.113 (2015): 20150702.

\bibitem[\protect\citeauthoryear{Feroz, Hobson,
\& Bridges}{2009}]{multinest} Feroz F., Hobson M.~P., Bridges M., 2009, MNRAS, 398, 1601

\bibitem[Giffin and Caticha(2007)]{giffin} Giffin, A., Caticha, A.\ 2007.\ Updating Probabilities with Data and Moments.\ Bayesian Inference and Maximum Entropy
Methods in Science and Engineering 954, 74-84.

\bibitem[\protect\citeauthoryear{Green}{1995}]{green}
Green, P.~J., 1995, Reversible Jump Markov Chain Monte Carlo Computation and Bayesian Model Determination, Biometrika 82 (4): 711–732.

\bibitem[Handley et al.(2015)]{2015MNRAS.453.4384H} Handley, W.~J., Hobson, M.~P., Lasenby, A.~N.\ 2015.\ POLYCHORD: next-generation nested sampling.\ Monthly Notices of the Royal Astronomical Society 453, 4384-4398.

\bibitem[Huppenkothen et al.(2015)]{2015ApJ...810...66H} Huppenkothen, D., Brewer, B.~J., Hogg, D.~W., Murray, I., Frean, M., Elenbaas, C., Watts, A.~L., Levin, Y., van der Horst, A.~J., Kouveliotou, C.\ 2015.\ Dissecting Magnetar Variability with Bayesian Hierarchical Models.\ The Astrophysical Journal 810, 66.

\bibitem[Neal(2003)]{slice}
Neal, R.M., 2003. Slice sampling. Annals of statistics, pp.705-741.

\bibitem[\protect\citeauthoryear{O'Hagan and Forster}{2004}]{ohagan}
O'Hagan, A., Forster,~J., 2004, Bayesian inference. London: Arnold.

\bibitem[Pancoast et al.(2014)]{2014MNRAS.445.3055P} Pancoast, A., Brewer, B.~J., Treu, T.\ 2014.\ Modelling reverberation mapping data - I. Improved geometric and dynamical models and comparison with cross-correlation results.\ Monthly Notices of the Royal Astronomical Society 445, 3055-3072.

\bibitem[\protect\citeauthoryear{Sivia and Skilling}{2006}]{sivia} Sivia, 
D.~ S., Skilling, J., 2006, Data Analysis: A Bayesian Tutorial, 2nd 
Edition, Oxford University Press

\bibitem[P{\'a}rtay et al.(2009)]{2009arXiv0906.3544P} P{\'a}rtay, L.~B., 
Bart{\'o}k, A.~P., Cs{\'a}nyi, G.\ 2009.\ Efficient sampling of atomic 
configurational spaces.\ ArXiv e-prints arXiv: 0906.3544.

\bibitem[Robert et al.(2011)]{robert}
Robert, C.P., Cornuet, J.M., Marin, J.M. and Pillai, N.S., 2011. Lack of confidence in approximate Bayesian computation model choice. Proceedings of the National Academy of Sciences, 108(37), pp.15112-15117.

\bibitem[\protect\citeauthoryear{Skilling}{2006}]{skilling} Skilling, J., 2006, Nested Sampling for General Bayesian Computation, Bayesian Analysis 4, pp. 833-860.

\end{thebibliography}

@@

The log likelihood is specified in {\tt julia\_model.jl}, as a function
called {\tt log\_likelihood} that takes a {\tt Vector::Float64} as an argument
and returns a {\tt Float64}. You should assume that the priors for the
parameters are independent Uniform(0, 1) distributions (sensible default
proposals are used). To use a different prior, transform the parameters inside
your {\tt log\_likelihood} function before using them.
You may add other functions to {\tt julia\_model.jl}, for example to load
a dataset to refer to in your {\tt log\_likelihood}. The example in
the repository is the ``SpikeSlab'' likelihood from \citet{dnest}.

>>>>

\documentclass[article, nojss]{jss}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{enumerate}
\usepackage{microtype}
\usepackage{dsfont}

@@

\section{Introduction}
Bayesian inference, where probability theory describes degrees of
logical implication or subjective certainty, provides a powerful general basis
for data analysis \citep{o2004kendall, sivia2006data}. The result of such
an analysis is typically
posterior probabilities of various hypotheses, or
a joint posterior probability distribution for the values of unknown
parameters.

@@

Nested Sampling \citep[NS;][]{skilling2006nested} is a Monte Carlo method whose main
aim is to calculate $Z$. However, it can also be used to generate samples
to represent the posterior distribution $\pi(\theta)L(\theta)/Z$, or
any other distribution proportional to
$\pi(\theta)\Phi\left[L(\theta)\right]$ where $\Phi$ is any monotonic function.
This latter property makes NS particularly useful for statistical mechanics
calculations \citep{partay2010efficient, baldock2016determining},
where the
``canonical'' family of distributions proportional to
$\pi(\theta)L(\theta)^\beta$ is of interest. In such applications,
$L(\theta)$ is usually equivalent to
$\exp(-\textnormal{energy})$. NS is particularly efficient for this, since
only a single run (exploring regions of higher and higher $L$) is needed, and different canonical
distributions can be obtained by re-weighting the output points.

@@

Sampling from the constrained priors (Equation~\ref{eqn:constrained_prior})
is required, and Markov Chain Monte Carlo (MCMC) is a popular method of doing
this, although alternatives exist
\citep[e.g.][]{feroz2009multinest, handley2015polychord}.
Diffusive Nested Sampling \citep[DNS;][]{brewer2011diffusive}
is an alternative to NS for
problems where MCMC is the only viable sampling method. DNS is based on the
Metropolis algorithm, and evolves one or more particles in the parameter space, along with
an integer index variable $j$ for each particle,
to explore the following joint distribution:
\begin{align}
p(\theta, j) &= p(j)p(\theta | j)\\
&= w_j \times
\frac{\pi(\theta)\mathds{1}\left[L(\theta) > \ell_j\right]}{X(\ell_j)}.
\label{eqn:target_distribution}
\end{align}
where the $\{\ell_j\}$ are a sequence of increasing likelihood thresholds
or {\em levels},
$\ell_0 = 0$, and $\{w_j\}$ is the marginal distribution for $j$.
The marginal distribution for $\theta$ is then a {\em mixture} of
constrained priors:
\begin{align}
p(\theta) &=
\pi(\theta)\sum_{j=0}^{j_{\rm max}}
\frac{w_j\mathds{1}\left[L(\theta) > \ell_j\right]}{X(\ell_j)}.
\label{eqn:mixture_of_constrained_priors}
\end{align}
The DNS algorithm consists of two stages. In the first stage,
the particle(s) are initialized from the prior $\pi(\theta)$, equivalent
to the mixture of constrained priors with a single level whose log likelihood
threshold is $-\infty$. The mixture of constrained priors evolves by adding new levels,
each of which compresses the distribution by a factor of about $e \approx 2.71818$
(see \citet{brewer2011diffusive} for details). In this stage,
the mixture weights $\{w_j\}$ are set according to
\begin{align}
w_j &\propto \exp(j/\lambda),\label{eqn:weighting}
\end{align}
where $\lambda$ is a scale length.
This enhances the probability that particles stay close to the
highest likelihood regions seen.
The second stage sets the mixture weights to be approximately
uniform ($w_j \propto 1$), with some tweaks described by
\citet{brewer2011diffusive}.

The mixture of constrained priors tends to be easier to sample than the
posterior, as the prior is always a mixture component, allowing the
MCMC chain to mix between different modes in some circumstances. The marginal
likelihood estimate can also be more accurate than standard MCMC-based NS
\citep{brewer2011diffusive}, as less information is discarded.
DNS has been applied several times in astrophysics
\citep[e.g.][]{pancoast2014modelling, huppenkothen2015dissecting,
brewer2015fast}
and was recently used in a biological application
\citep{dybowski2015single}.

@@

The second column contains the log likelihoods of the levels.
The first level, with a $\log(X)$ value of 0 and a log likelihood of
$-10^{308}$ (basically ``minus infinity''), is simply the prior. The third
column has the ``tiebreaker'' values for the levels, which again are not
particularly useful unless your problem has likelihood plateaus. The fourth
and fifth columns are the number of accepted proposals and the total number
of proposals that have occurred within each level, which are useful for
monitoring the Metropolis acceptance ratio as a function of level.
The final two columns, called ``exceeds'', and ``visits'', are used to refine
the estimates of the level compressions (and hence the $\log(X)$ values of
the levels in column 1), as discussed in Section 3 of
\citet{brewer2011diffusive}.
The visits column counts the number of times a level (level $j$, say)
has been visited, but only starts counting after the next level ($j+1$) has been created. The exceeds column counts the number of times a particle that was
in level $j$ had a likelihood that exceeded that of level $j+1$.

@@

As described by \citet{skilling2006nested}, there is no guarantee in principle that
another peak might have appeared had a run continued for longer. These
{\em phase changes} are more common in statistical mechanics problems than
in data analysis problems, but can appear in the latter
\citep[e.g.][]{brewer2014inference, brewer2015fast}.

@@

\subsection{Equal weight enforcement}
This value is the parameter $\beta$ described in
\citet{brewer2011diffusive}, and compensates
for imprecision in the spacing of the levels, so that the desired mixture
weights $w_j \propto 1$ are achieved during the second stage of the DNS
algorithm. The value 100 is recommended.

@@

Rather than trying to adapt proposal distributions as a function of level,
it is much simpler to just use heavy-tailed proposals which have some
probability of making a jump of appropriate size. This is slightly
wasteful of CPU time, but it saves a lot of human time and is more
fail-safe than tuned step sizes.
In simple experiments, we have found that heavy-tailed proposals are
about as efficient as slice sampling \citep{neal2003slice}, but much easier to
implement. The following procedure generates
$x$ from a heavy-tailed distribution:

@@

\section{Finite Mixture Models with RJObject}
Mixture models are a useful way of representing realistic prior information
in Bayesian data analysis. To reduce the amount of effort needed to
implement mixture models in DNS, \citet{brewer2014inference} implemented
a template class called \code{RJObject} to handle the MCMC moves
required. The RJ in \code{RJObject} stands for Reversible Jump
\citep{green1995reversible}, as
\code{RJObject} implements birth and death moves for mixture
models with an unknown number of components. An updated version of
\code{RJObject} is included in \pkg{DNest4}.

@@

\citet{brewer2014inference}
described the motivation for \code{RJObject} and some details
about the Metropolis proposals underlying it. Here, we demonstrate how to
implement a finite mixture model using \code{RJObject}.
This example can be found in the
{\tt code/Examples/RJObject\_1DMixture}
directory. The ``SineWave'' and ``GalaxyField'' models
from \citet{brewer2014inference}
are also included in the \pkg{DNest4} repository.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=0.7\textwidth]{figures/galaxies_fig3.pdf}
\caption{The log-likelihood and posterior weights as a function
of compression $X$ for the galaxy data. There are phase changes
\citep{skilling2006nested} for which Nested Sampling is the best known
solution.
\label{fig:galaxies_fig3}}
\end{figure}

@@

A simple ``rejection sampling'' version of
ABC works by sampling the joint prior distribution for the parameters and
data
\begin{align}
p(\theta, D | M) &= p(\theta | M)p(D | \theta, M)
\end{align}
and rejecting samples for which $D \neq D_{\rm observed}$, so that the
samples represent
\begin{align}
p(\theta, D | D = D_{\rm observed}, M) &\propto p(\theta | M)p(D | \theta, M)
\mathds{1}\left[D = D_{\rm observed}\right].\label{eqn:abc_posterior}
\end{align}
The marginal distribution for $\theta$ is also the conditional distribution
$p(\theta | D = D_{\rm observed}, M)$, that is,
the posterior\footnote{Incidentally, this usage of the {\em joint} posterior
distribution for the parameters {\em and the data} provides a bridge
connecting Bayesian updating to maximum entropy updating
\citep{caticha2006updating,giffin2007updating}.}.

@@

The main challenges associated with ABC are:
\begin{enumerate}[(i)]
\item The choice of discrepancy function $\rho(D; D_{\rm observed})$, which
may involve a choice of summary statistics,
\item How to choose the value of $\epsilon$, or how to change it as a run
progresses,
\item How to make algorithms more efficient than rejection sampling.
\end{enumerate}
Challenge (i) is Bayesian in nature, i.e. it relates to the very
definition of the posterior distribution itself.
On the other hand, challenges (ii) and (iii) are about the computational
implementation. Most ABC analyses are done using Sequential Monte Carlo
\citep[SMC; ][]{del2012adaptive}, another family of algorithms closely related
to Nested Sampling and annealing in the sense that they work with
sequences of probability distributions.

\subsection{ABC with Nested Sampling}
NS can be used for ABC by noting that Equation~\ref{eqn:abc_posterior}
is of the same form as a constrained prior, only instead of being the prior
for the parameters $p(\theta | M)$ defined on the parameter space, it is
the {\em joint prior} for the parameters and the data,
$p(\theta, D |M) = p(\theta | M)p(D | \theta, M)$, defined on the product
space of possible parameters and datasets. Therefore, to implement
ABC in \pkg{DNest4}, you implement a model class
whose \code{from\_prior} member function generates parameters {\em and simulated
data} from the joint prior, and whose \code{perturb} member function
proposes changes to the parameters and/or the simulated data, in a
manner consistent with the joint prior. The \code{log\_likelihood} function
of the class, instead of actually evaluating the log likelihood, should
evaluate $-\rho(D; D_{\rm observed})$. Then, running the sampler
will create levels which systematically decrease $\rho$. The samples from
a particular level then represent the ABC posterior defined in
Equation~\ref{eqn:abc_posterior} with $\epsilon$ corresponding to minus
the ``log likelihood'' of the level.
A single \pkg{DNest4} run allows you to test sensitivity
to the value of $\epsilon$ using a single run.
The marginal likelihood reported will be
the probability that $\rho\left(D; D_{\rm observed}\right) < \epsilon$
given the model, although caution should be applied if
using this for model selection \citep{robert2011lack}.

@@

\bibliography{references}

@@

The log likelihood is specified in {\tt julia\_model.jl}, as a function
called {\tt log\_likelihood} that takes a {\tt Vector::Float64} as an argument
and returns a {\tt Float64}. You should assume that the priors for the
parameters are independent Uniform(0, 1) distributions (sensible default
proposals are used). To use a different prior, transform the parameters inside
your {\tt log\_likelihood} function before using them.
You may add other functions to {\tt julia\_model.jl}, for example to load
a dataset to refer to in your {\tt log\_likelihood}. The example in
the repository is the ``SpikeSlab'' likelihood from
\citet{brewer2011diffusive}.
